New Biomass Pools Workflow

### 2023-10-04 NewBiomassPoolsWorkflow.Rmd
outline next steps done and in progress

With an if statement?

@@

>>>>

With an if statement? Or let the species selection take care of that.

Decision: add it and if no biomass pools species selected it should return nothing

Added to `run_truth`:

+  area using existing `load_boxarea`
+  pooln using existing `load_nc` with select_variable = "N"
+  biomass_pools using new `calc_biomass_pool`

Returns biomass_pools as part of truth list

@@

In `om_species` need to check for biomass pools output and append that to the `truebio_ss` object? If one object can use existing `om_index` on bio pools.

```{r}
  # biomass at agecl at full resolution (all polygons and layers)
  #truebio_ss <- omlist$truth$biomass_ages[omlist$truth$biomass_ages$species %in% species_ss,]
```

If a single true bio object is created, may have to modify selectivty definition for biomass pools in `om_index`
